Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/Thailand_Healthcare]

### 2022-03-31 outputs/paper/paper.Rmd
data cleaning
ggplot

@@

# This needs to be about the random data tha tI sasmpled?
ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = FALSE) +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

>>>>

```{r}
data %>%
  ggplot(aes(x = Variable, y = Health_Record)) +
  geom_bar(stat='identity') +
  coord_flip()
```

@@
